---
name: Ugyen
surname: Norbu
position: "Transporttion Engineer"
address: "Road Safety & Transport Authority"
phone: +975 77364637
www: www.rsta.gov.bt
email: "unorbu@rsta.gov.bt"
twitter: Ugyen2007Norbu
github: UgyenNorbu
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 383838
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Work Experience
```{r}
library(tibble)
library(readxl)

data <- readxl::read_xlsx("/Users/ugyennorbu/Documents/GitHub/CV/data/work_exp.xlsx")

tibble(data) %>% 
  detailed_entries(Position, Year, Agency, Location)


```


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Engineering", "2017-19", "Anna University", "Chennai, India",
  "B.Tech in Civil Engineering", "2007-11", "Jaypee University of Information Technology", "HP, India"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Achievement

- Received Nehru-Wangchuk Scholarship in 2017 to pursue Masters in Engineering.
- Received YDF Academic Scholarship in 2007 to pursue B.Tech.
- Received Certificate of Excellence in 2005 for academic general proficiency from Yangchenphu Higher Secondary School
- Received Letter of Appreciation from Dzongdag, Pemagatshelthe for service rendered as National Observer during 2016 Local Government Election 

# Skills

- Data analysis and visualization using R and Python programming language.
- Drafting and engineering drawing using AutoCAD.
- Geospatial analysis and cartography using QGIS.
- Image editing using Photoshop, Gimp, Adobe Lightroom.
- 3D modeling using Google Sketchup.

# Additional information

- Attended training on ‘Urban Road Management and Maintenance’ in Sapporo, Japan in 2014 organised by JICA.
- Attended seminar on ‘Safe Mobility & Regional Connectivity’ in New Delhi, India organized by SASEC.
